### 2018-12-09 paper/paper.tex
adding abstract

%
% Generic Template
% Created on 11/6/2017 by Jonathan Chen
%

\documentclass[12pt]{article}
\usepackage[left=0.8in,right=0.8in,top=0.8in,bottom=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}                  % for header
\usepackage{graphicx}                  % for figures
\usepackage{amsmath}                   % for extented math markup
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{minted}
\usepackage{enumitem}
\usepackage{csquotes}
\usepackage{caption}
\usepackage{lipsum}
\usepackage[bookmarks=false]{hyperref} % for URL embedding
\usepackage{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\course}{CSE416A}
\newcommand{\names}{Benjamin Lai, Cate Jiang, and Jonathan Chen}

% create sheader and footer for every page
\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{Legislative Complex Networks}}
\chead{}
\rhead{Lai, Jiang, and Chen}
\cfoot{\thepage}

% environment for cases
\newlength\mylen
\settowidth\mylen{\textbf{Case~5.}}
\newlist{enumcases}{enumerate}{1}
\setlist[enumcases,1]{label=\textbf{Case~\arabic*.},leftmargin=0pt,align=right,%
    labelwidth=\dimexpr-\mylen-\labelsep\relax,}

% images
\captionsetup[figure]{
  font={footnotesize,singlespacing},
  labelfont=bf,
  singlelinecheck=off,
  justification=raggedright,
  labelsep=period
}

\newcommand{\image}[5][0.6]{
  % 1 - path to asset
  % 2 - label
  % 3 - title
  % 4 - caption
  \begin{figure}[H]
    \centering
    \includegraphics[width=1.0\textwidth,height=#1\textwidth,keepaspectratio]{#2}
    \caption[(details)]{\textbf{#4}. #5}
    \label{fig:#3}
  \end{figure}}

% minted
\usemintedstyle{pastie}
\setminted[python]{frame=lines,linenos,autogobble,framesep=1.4em,breaklines,%
                   escapeinside=||,mathescape,python3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% the document begins here!

\title{Comparative Analysis of Legislative Complex Networks of Select North American and European Countries}
\author{\names}
\date{December 11, 2018}

\begin{document}
\maketitle
% \vspace{0.1em}
\thispagestyle{empty}

\begin{center}
  \url{https://github.com/jowch/CSE-416-Final-Project}
\end{center}

\begin{abstract}
    Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries. To do so, we performed complex network analysis on North Amerian and European countries to understand how a wide variety political parties interacted with respect to cosponshorship. 
\end{abstract}

\section{Introduction}

\newpage

\section{Introduction}

\end{document}

### 2018-12-09 paper/paper.tex
moved repository link to authors
updating paper

@@
     Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries.
-To do so, we performed complex network analysis on North Amerian and European countries to understand how a wide variety political parties interacted with respect to cosponshorship.
+To do so, we performed complex network analysis on North Amerian and European countries to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship.
+    % To-do: Finish abstract %
 \end{abstract}
@@
 
+\section{Methods}
+\subsection{Data Collection}
+Cosponsorship data was taken from the following resources: \underline{Bill cosponshorship network} \cite{briatte}, \underline{Cosponsorship Network} \cite{fowler}, \underline{UK Parliament} \cite{UK}, and \underline{United States Congress} \cite{US}.
+
+\section{Results}
+
+\section{Discussion}
+
 \newpage
+\begin{thebibliography}{9}
 
-\section{Introduction}
+\bibitem{briatte} Briatte, Francois. 2016. ``Bill cosponsorship networks in European parliaments.'' \url{https://github.com/briatte/parlnet}.
+
+\bibitem{fowler} Fowler, J. H., Waugh, A.S., and Sohn, Y. 2010. ``Cosponsorship Network.'' \url{http://jhfowler.ucsd.edu/cosponsorship.htm}
+
+\bibitem{UK} UK Parliament. \url{https://edm.parliament.uk/}
+
+\bibitem{US} United States Congress. \url{https://github.com/unitedstates/congress}
+\end{thebibliography}
 

### 2018-12-09 lib/analysis/stats.py
changed imports in stats

@@ -1,10 +1,8 @@
 import graph_tool.all as gt
 import numpy as np
 from functools import reduce
-from lib.analysis import clustering
-from lib.analysis import dist
-from lib.analysis import model
-from lib.analysis import power
+from .clustering import coefficient as clustering_coefficient
+from .dist import degree, excess_degree
 
 
 class Summary:
@@ -67,13 +65,13 @@ def summary(g: gt.Graph):
     num_vertices = g.num_vertices()
     
     # Clustering coefficient
-    clustering_coefficient = clustering.coefficient(g)
+    clustering_coeff = clustering_coefficient(g)
 
     # Average degree
-    _, avg_degree = dist.degree(g, report_avg=True)
+    _, avg_degree = degree(g, report_avg=True)
     
     # Average excess degree
-    _, avg_excess_degree = dist.excess_degree(g, report_avg=True)
+    _, avg_excess_degree = excess_degree(g, report_avg=True)
     
     # Size of largest connected component
     l = gt.label_largest_component(g)
@@ -90,7 +88,7 @@ def summary(g: gt.Graph):
     data = {
         'Number of Edges': num_edges,
         'Number of Vertices': num_vertices,
-        'Clustering Coefficient': clustering_coefficient,
+        'Clustering Coefficient': clustering_coeff,
         'Average Degree': avg_degree,
         'Average Excess Degree': avg_excess_degree,
         'Average Distance': avg_path,

### 2018-12-09 lib/analysis/centrality.py
centrality measures

@@ -1,11 +1,20 @@
 import graph_tool.all as gt
 
-
-def betweenness(g: gt.Graph) -> (gt.PropertyMap, gt.PropertyMap):
-    '''returns both vertex and edge betweenness'''
-    vertex, edge = gt.betweenness(g, norm=True)
+def betweeness(g: gt.Graph) -> (gt.PropertyMap, gt.PropertyMap):
+    '''returns both vertex and edge betweeness'''
+    vertex, edge = gt.betweeness(g, norm=True)
     return vertex, edge
 
+def closeness(g: gt.Graph) -> gt.PropertyMap:
+    '''returns vertex closeness'''
+    vertex = gt.closeness(g, norm=True)
+    return vertex
+
+def eigenvector(g: gt.Graph) -> (np.float6, gt.Propertymap):
+    '''returns eigenvector and largest eigvenvalue'''
+    value, vector = gt.eigenvector(g)
+    return value, vector
 
 if __name__ == '__main__':
     pass
+

### 2018-12-09 lib/analysis/stats.py
added assortivity function

@@ -5,6 +5,11 @@ from .clustering import coefficient as clustering_coefficient
 from .dist import degree, excess_degree
 
 
+def assortativity(g: gt.Graph, attribute_map: gt.PropertyMap) -> np.float:
+    coeff, _ = gt.assortativity(g, attribute_map)
+    return coeff
+
+
 class Summary:
     def __init__(self, data: dict):
         self.data = data

### 2018-12-09 lib/analysis/centrality.py
corrected centrality imports

@@ -1,4 +1,5 @@
 import graph_tool.all as gt
+import numpy as np
 
 def betweeness(g: gt.Graph) -> (gt.PropertyMap, gt.PropertyMap):
     '''returns both vertex and edge betweeness'''
@@ -10,7 +11,7 @@ def closeness(g: gt.Graph) -> gt.PropertyMap:
     vertex = gt.closeness(g, norm=True)
     return vertex
 
-def eigenvector(g: gt.Graph) -> (np.float6, gt.Propertymap):
+def eigenvector(g: gt.Graph) -> (np.float64, gt.PropertyMap):
     '''returns eigenvector and largest eigvenvalue'''
     value, vector = gt.eigenvector(g)
     return value, vector

### 2018-12-09 paper/paper.tex
adding intro and data collection

@@
 \title{Comparative Analysis of Legislative Complex Networks of Select North American and European Countries}
-\author{\names}
+\author{\names \\ \small\url{https://github.com/jowch/CSE-416-Final-Project}}
+
 \date{December 11, 2018}
@@
 
-\begin{center}
-  \url{https://github.com/jowch/CSE-416-Final-Project}
-\end{center}
-
 \begin{abstract}
@@
 To do so, we performed complex network analysis on North Amerian and European countries to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship.
+We found summary statistics for each of the countries and plotted different centrality measures for comparison.
     % To-do: Finish abstract %
@@
 
+In the United States, politics has increasingly become a point of conversation due to change of presidency and new bills being signed into laws.
+Cosponshorship provides a rich network between legislators that can be used to explain the political effects and efficiency of legislative processes.
+We propose to analyze the networks of different legislative bodies in select North American and European countries to determine how legislators interact amongst each other to cosponsor bills.
+We aim to answer questions such as which countries' legislators are most connected, how legislative parties and other attributes play into cosponsorship data, and what that means in terms of government performance and productivity.
+To perform our research, we will use cosponsorship data from different countries followed by analysis and comparison of statistics and centrality measures.
+
+According a study conducted by James Folwer from the Department of Political Science at the University of California, Davis, there are several trends that have been observed among legislators.
+In the United States, biennial elections cause members of the U.S.
+House and Senate to change every two years, but the trends remain stable.
+Firstly, party affiliation and similar values and ideals often lead to increased possibility of cosponsorship.
+Second, average number of cosponsors per legislator reflects the degree that the individual is integrated into their political network \cite{fowler1}.
+Because these studies were performed solely within U.S.
+Congression, we propose to analyze legislators from different first-world countries to determine if these trends would be observed in other political environments as well.
+
 \section{Methods}
-\subsection{Data Collection}
-Cosponsorship data was taken from the following resources: \underline{Bill cosponshorship network} \cite{briatte}, \underline{Cosponsorship Network} \cite{fowler}, \underline{UK Parliament} \cite{UK}, and \underline{United States Congress} \cite{US}.
 
-\section{Results}
+\subsection{Data Collection and Pre-Processing}
+We first obtained cosponsorship data for the countries: Austria, Denmark, France, Sweden, Switzerland, United Kingdom, and the United States.
+This was taken taken from the following resources: \underline{Bill cosponshorship} \cite{briatte}, \underline{Cosponsorship Network} \cite{fowler}, \underline{UK Parliament} \cite{UK}, and \underline{US Congress} \cite{US}.
+The raw data was parsed and saved as \texttt{graphml} files.
+Because the data from many databases were divided based on years, we also had to load and combine various \texttt{graphml} files to create a single network for each country we were analyzing.
+The data is stored in \texttt{CSE-416-Final-Project/data/} in our repository.
 
-\section{Discussion}
+\subsection{Data Analysis}
+We created a function
+
+\section{Results and Discussion}
 
@@
 
-\bibitem{briatte} Briatte, Francois. 2016. ``Bill cosponsorship networks in European parliaments.'' \url{https://github.com/briatte/parlnet}.
+\bibitem{briatte} Briatte, Francois. ``Bill cosponsorship networks in European parliaments.'' 2016. \url{https://github.com/briatte/parlnet}.
 
-\bibitem{fowler} Fowler, J. H., Waugh, A.S., and Sohn, Y. 2010. ``Cosponsorship Network.'' \url{http://jhfowler.ucsd.edu/cosponsorship.htm}
+\bibitem{fowler1} Fowler, James H. ``Connecting the Congress: A Study of Cosponsorship Network.'' 2006. \url{http://fowler.ucsd.edu/best_connected_congressperson.pdf}
+
+\bibitem{fowler} Fowler, J. H., Waugh, A.S., and Sohn, Y. ``Cosponsorship Network.'' 2010. \url {http://jhfowler.ucsd.edu/cosponsorship.htm}
 

### 2018-12-10 lib/analysis/stats.py
assortativity

@@ -9,6 +9,13 @@ def assortativity(g: gt.Graph, attribute_map: gt.PropertyMap) -> np.float:
     coeff, _ = gt.assortativity(g, attribute_map)
     return coeff
 
+def assortativity_summary(g: gt.Graph, label: str):
+    '''Returns a summary of graph assortivity on given label'''
+    coeff = assortativity(g, g.vertex_properties[label])
+    data = {
+    'Assortivity on: ' + label: coeff,
+    }
+    return Summary(data)  
 
 class Summary:
     def __init__(self, data: dict):
@@ -25,6 +32,7 @@ class Summary:
 
     def get_headers(self):
         return ','.join(self.data.keys())
+    
 
 
 def num_components(g: gt.Graph):

### 2018-12-10 lib/analysis/stats.py
generated party_id property map

@@ -4,6 +4,17 @@ from functools import reduce
 from .clustering import coefficient as clustering_coefficient
 from .dist import degree, excess_degree
 
+def generate_party_property(g: gt.Graph, label: str):
+    partyMap = {}
+    out = []
+    parties = [party for party in g.vertex_properties[label]]
+    d = dict([(y,x+1) for x,y in enumerate(sorted(set(parties)))])
+    for party in parties:
+        out.append(d[party])
+    party_id = g.new_vertex_property("int32_t")
+    for i in range(len(out)):
+        party_id[g.vertex(i)] = out[i]
+    g.vertex_properties['party_id'] = party_id
 
 def assortativity(g: gt.Graph, attribute_map: gt.PropertyMap) -> np.float:
     coeff, _ = gt.assortativity(g, attribute_map)

### 2018-12-10 lib/analysis/stats.py
fixed assortativity bug

@@ -26,7 +26,8 @@ def assortativity_summary(g: gt.Graph, label: str):
     data = {
     'Assortivity on: ' + label: coeff,
     }
-    return Summary(data)  
+#     return Summary(data)  
+    return coeff
 
 class Summary:
     def __init__(self, data: dict):

### 2018-12-10 lib/analysis/stats.py
modified lib stats

@@ -56,16 +56,17 @@ def num_components(g: gt.Graph):
 
 
 def average_distance(g: gt.Graph):
-    _, components = num_components(g)
+    nc, components = num_components(g)
     sums, counts = [], []
 
     for component in components:
-        ds = np.array(list(gt.shortest_distance(component)))
-        count = ds[ds > 0].shape[0] / 2
-        sums.append(np.sum(ds) / 2)
-        counts.append(count)
+        if component.num_vertices() > 1:
+            ds = np.array(list(gt.shortest_distance(component)))
+            count = ds[ds > 0].shape[0] / 2
+            sums.append(np.sum(ds) / 2)
+            counts.append(count)
 
-    return sum(sums) / sum(counts)
+    return 0 if nc == g.num_vertices() else sum(sums) / sum(counts)
 
 
 def summary(g: gt.Graph):

### 2018-12-10 lib/analysis/stats.py
updated assortivity

@@ -26,8 +26,7 @@ def assortativity_summary(g: gt.Graph, label: str):
     data = {
     'Assortivity on: ' + label: coeff,
     }
-#     return Summary(data)  
-    return coeff
+    return Summary(data)  
 
 class Summary:
     def __init__(self, data: dict):

### 2018-12-10 lib/analysis/dist.py
fixed average degree computation

@@ -2,17 +2,17 @@ import numpy as np
 import graph_tool.all as gt
 
 
-def degree(g: gt.Graph, deg='total', report_avg=False):
+def degree(g: gt.Graph, deg='total'):
     '''
     Returns array of degree frequencies.
     '''
     degrees = g.degree_property_map(deg=deg).a
     counts = np.bincount(degrees)[1:]
-    pdf = counts / np.sum(counts)
-    k = np.arange(counts.shape[0]) + 1
-    return pdf, np.dot(k, pdf) if report_avg else pdf
+    pdf = counts / counts.sum()
+    k = np.arange(degrees.max()) + 1
+    return pdf, np.dot(k, pdf)
 
-def excess_degree(g: gt.Graph, deg='total', report_avg=False):
+def excess_degree(g: gt.Graph, deg='total'):
     '''
     Returns array of excess degree frequencies.
     '''
@@ -30,10 +30,11 @@ def excess_degree(g: gt.Graph, deg='total', report_avg=False):
     k = np.arange(1, degrees.max() + 1)
     counts = q(k)
     pdf = counts / np.sum(counts)
-    return pdf, np.dot(k, pdf) if report_avg else pdf
+    return pdf, np.dot(k, pdf)
 
 def power(g: gt.Graph, a_hat, k_min=1):
-    k = np.arange(1, degree(g).max())
+    degrees = g.degree_property_map('total')
+    k = np.arange(1, degrees.max())
     return (a_hat - 1) / k_min * np.power(k / k_min, -a_hat)
 
 

### 2018-12-10 lib/analysis/stats.py

@@ -93,10 +93,10 @@ def summary(g: gt.Graph):
     clustering_coeff = clustering_coefficient(g)
 
     # Average degree
-    _, avg_degree = degree(g, report_avg=True)
+    _, avg_degree = degree(g)
     
     # Average excess degree
-    _, avg_excess_degree = excess_degree(g, report_avg=True)
+    _, avg_excess_degree = excess_degree(g)
     
     # Size of largest connected component
     l = gt.label_largest_component(g)

### 2018-12-10 lib/analysis/centrality.py
centrality graphs

@@ -1,19 +1,27 @@
 import graph_tool.all as gt
 import numpy as np
 
-def betweeness(g: gt.Graph) -> (gt.PropertyMap, gt.PropertyMap):
+def betweenness(g: gt.Graph, scale=None) -> (gt.PropertyMap, gt.PropertyMap):
     '''returns both vertex and edge betweeness'''
-    vertex, edge = gt.betweeness(g, norm=True)
+    vertex, edge = gt.betweenness(g, norm=True)
+    if scale:
+        vertex = g.new_vp('float', vertex.a * scale)
+        edge = g.new_ep('float', edge.a * scale)
     return vertex, edge
 
-def closeness(g: gt.Graph) -> gt.PropertyMap:
+def closeness(g: gt.Graph, scale=None) -> gt.PropertyMap:
     '''returns vertex closeness'''
     vertex = gt.closeness(g, norm=True)
+    if scale:
+        vertex = g.new_vp('float', vertex.a * scale)
     return vertex
 
-def eigenvector(g: gt.Graph) -> (np.float64, gt.PropertyMap):
+def eigenvector(g: gt.Graph, scale=None) -> (np.float64, gt.PropertyMap):
     '''returns eigenvector and largest eigvenvalue'''
     value, vector = gt.eigenvector(g)
+    if scale:
+        value *= scale
+        vector = g.new_vp('float', vector.a * scale)
     return value, vector
 
 if __name__ == '__main__':

### 2018-12-11 paper/paper.tex
editing methods
adding graphing_trends
adding average trends across countries

@@
     Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries.
-To do so, we performed complex network analysis on North Amerian and European countries to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship.
-We found summary statistics for each of the countries and plotted different centrality measures for comparison.
+To do so, we performed complex network analysis on seven North Amerian and European countries (Austria, Denmark, France, Sweden, Switerland, UK, and US) to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship.
+We found and plotted summary statistics and centrality measures to make comparisons possible.
     % To-do: Finish abstract %
@@
 
-\section{Methods}
+\section{Materials and Methods}
 
@@
 Because the data from many databases were divided based on years, we also had to load and combine various \texttt{graphml} files to create a single network for each country we were analyzing.
-The data is stored in \texttt{CSE-416-Final-Project/data/} in our repository.
+The data is stored in \texttt{CSE-416-Final-Project/data/} and the pre-processing was performed in the \texttt{Analysis} file in the root directory within our repository.
 
 \subsection{Data Analysis}
-We created a function
 
-\section{Results and Discussion}
+\section{Results}
+
+\section{Discussion}
 

### 2018-12-11 paper/paper.tex
adding potential results

@@
 We found and plotted summary statistics and centrality measures to make comparisons possible.
-    % To-do: Finish abstract %
 \end{abstract}
@@
 \section{Results}
+\begin{itemize}
+  \item Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but one of the smallest number of edges (large number of people but very few connections made between them in comparison to other countries)
+  \item Average Degree: US has average degree which is much higher than the average degree for other countries (each node is very highly connected to many other nodes)
+  \item Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to other countries but has the second smallest average distance (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
+  \item Comparison of Size of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US are very highly connected and only has a few connected components)
+\end{itemize}
 

### 2018-12-11 paper/paper.tex

@@
   \item Average Degree: US has average degree which is much higher than the average degree for other countries (each node is very highly connected to many other nodes)
+  \item Comparison of Average Degree and Average Excess Degree: UK has one of the lowest average degrees but has the second largest average excess degree.
+This means that although each node is not connected to many other nodes, it is on average connected to other important nodes.
+This is a contrast between US and Denmark where their average degree and average excess degrees are relatively similar.
   \item Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to other countries but has the second smallest average distance (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
-  \item Comparison of Size of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US are very highly connected and only has a few connected components)
+  \item Comparison of Size of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US are very highly connected and only has a few connected components).
+In comparison, France has an average size of LCC that is slightly lower than the average of all countries, but it has the highest number of CC.
 \end{itemize}

### 2018-12-11 paper/paper.tex
editing paper and adding assortativity graph

@@
     Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries.
-To do so, we performed complex network analysis on seven North Amerian and European countries (Austria, Denmark, France, Sweden, Switerland, UK, and US) to understand how a wide variety political parties interacted amongst each other with respect to cosponshorship.
+To do so, we performed complex network analysis on seven North Amerian and European countries (Austria, Denmark, France, Sweden, Switerland, UK, and US) to understand how a wide variety political parties interacted amongst each other with respect to cosponsorship.
 We found and plotted summary statistics and centrality measures to make comparisons possible.
@@
 In the United States, politics has increasingly become a point of conversation due to change of presidency and new bills being signed into laws.
-Cosponshorship provides a rich network between legislators that can be used to explain the political effects and efficiency of legislative processes.
+Cosponsorship provides a rich network between legislators that can be used to explain the political effects and efficiency of legislative processes.
 We propose to analyze the networks of different legislative bodies in select North American and European countries to determine how legislators interact amongst each other to cosponsor bills.
@@
 
+%TODO: scraping
+
 \subsection{Data Analysis}
 
+Our analysis was performed using a library called \href{https://graph-tool.skewed.de}{graph-tool}, which provides Python bindings to powerful abstractions and parallel algorithms for processing graphs.
+In addition, we used \texttt{numpy}, \texttt{scipy}, \texttt{pandas}, \texttt{seaborn}, and \texttt{matplotlib} to perform the comparative analysis.
+
+We wrote a summary function that returns a summary of graph statistics with a given graph.
+These statistics include: number of edges, number of vertices, average clustering coefficient, average degree, average excess degree, average path length, size of largest connected component, and number of connected components.
+We then wrote a script that produces a summary output in a csv file for every country for every year.
+
+An important attribute of our generated networks that we needed to measure was assortativity.
+Each graph had various vertex properties to perform assortativity measures on, but we decided to use `party' to determine whether governments cooporate on a partison or bipartison basis.
+We mapped each `party' to a unique ID, and joined this party enumeration property map with the original vertex properties.
+We then produced graphs for every country across each year, with nodes colored based off their respective enumerated `party' property map.
+
+Betweenness, closeness, and eigenvector centrality measures were also performed on our data to identify influential legislators.
+The graphed vertices and edges were scaled and colored with respect to its corresponding centrality measure.
+Vertices and edges that are yellow and larger in size reflect greater importance, whilst those that are blue and smaller in size reflect lesser importance.
+For the generated betweenness graphs, the top 3 percent of legislators with the highest betweenness centralities were colored yellow and enlarged.
+
 \section{Results}
+\subsection{Country-level Results}
+\begin{itemize}
+  \item Every country we look at has some sort of temporal data except for Denmark and the UK.
+Explain why we don't have the data because of how the database worked.
+But we still performed the same summary statistics and produced graphs.
+  \item Austria - the number of edges and vertices do not fluctuate between the years for most countries.
+Number of vertices around 63.
+Average degree has been relatively stable, which is expected given the lack of change in edges and vertices.
+Excess degree decreases from 1995 to 1999.
+The excess degree dropped to around 2, which is similar to the average degree for Austria.
+This happens to coincide with Austria joining the European Union in 1995.
+It is unclear whether there is a correlation between joining the EU and the sharp decrease in average excess degree.
+However, it can be noted that the drop in excess degrees leads to a similar value as the average degree, which means that the degree of individuals are roughly the same as the degree of their neighbors on average.
+This also means there is less or almost no hub behavior.
+  % To-do: clustering coefficient is 0 for years 94-95, 06-08, 13-18 but we don't know why -- show plots
+  \item France has had a steady increase of vertices.
+It started with a little less than 300 verticies in 1986-1988, and now it is around 500.
+Its number of edges peaked during 2002-2007 to 16,000 from 1986-1988 which had 2,000 edges.
+(During the same time, the clustering coefficient has increased by 1/3.) The average distance has not decreased by much, which is surprising given the amount of increase in vertices.
+  % To-do: figure out what clustering coefficient means
+  \item UK - Number of averages vertices (675) is greater than the average number of edges (663).
+This means that in general, a node has slightly less than one connection.
+The average excess degree is greater than 200, which is greater than 100 times the average degree, which is roughly 2.0.
+This can also be explained when observing a subset of the betweenness graph of UK.
+The majority of the UK betweenness graph has a single node that is connected to many other nodes that only has one edge.
+  \image[0.2]{Images/uk-betweenness.png}{}{}{}
+  \item Denmark - there are 2 themes that have the most number of vertices, which are economy and justice.
+According to Forbes in December 2017, Denmark is known for its extremely efficient economy and equitable distribution of income.
+It is also currently undergoing an economic expansion.
+Denmark is also rated \#1 for least corruption \cite{denmark}.
+Given this information, it is expected that Denmark would have the most legislators responsible for Economy and Justice.
+  \item Switzerland - there exists few changes in Switzerland's graph statistics over the years.
+The country's clustering coefficient remains consistently around 0.5, and its number of vertices around 130 and its number of edges around 1750.
+  \item Sweden - there is an interesting change in the number of cosponsorships across parties between the years 2014-2018.
+The number of vertices across years consistently hover around 350, whereas the number of edges dropped from 4000 in 1988-1991 to 2000 in 2014-2018.
+This result happens to coincide with an event during the 2014 Swedish general election, in which the Social Democrats declared that they would not work with the Sweden Democrats.
+This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018.
+  \image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{}{}{}
+  \image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{}{}{}
+  \item US - The US had extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (roughly 400).
+This shows that although members change every 2 years, the legislators and their interactions are relatively stable.
+\end{itemize}
+
+\subsection{Across-Country Results}
 \begin{itemize}
@@
   \item Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to other countries but has the second smallest average distance (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
-  \item Comparison of Size of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US are very highly connected and only has a few connected components).
+  \item Comparison of Size of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US nodes are very highly connected and only has a few connected components).
 In comparison, France has an average size of LCC that is slightly lower than the average of all countries, but it has the highest number of CC.
+  \item US graph is almost completely connected.
+Fully connected graphs have $n(n-1)/2$ edges.
+There are about 100,000 edges and 552 vertices.
+A complete graph would have 152,076.
+So this is about 67\%.
 \end{itemize}
@@
 \section{Discussion}
+For our project, we use legislative cosponsorship networks across the US and selected European countries to try to infer social relationships in government that may influence legislative behavior.
+How well officials work together has a direct impact on the efficiency and productivity of government.
+The dynamic social relationships between legislators - of forging new relationships and maintaining older established relationships - matter.
+We have uncovered some intriguing results. First, we notice that the average distance tends to increase as the world gets smaller.
+
+there exists an inverse relationship between the size of a graph and its average distance.
 
@@
 
-\bibitem{fowler1} Fowler, James H. ``Connecting the Congress: A Study of Cosponsorship Network.'' 2006. \url{http://fowler.ucsd.edu/best_connected_congressperson.pdf}
+\bibitem{denmark} ``Denmark.'' \emph{Forbes}, Forbes Magazine, \url{www.forbes.com/places/denmark/}
+
+\bibitem{fowler1} Fowler, James H. ``Connecting the Congress: A Study of Cosponsorship Network.'' 2006. \url{http://fowler.ucsd.edu/best_connected_congressperson.pdf}.
 

### 2018-12-11 paper/paper.tex
updating paper

@@
 \usepackage{hyperref}
+\usepackage{wrapfig}
+\usepackage{multicol}
 
@@
 
-\newcommand{\image}[5][0.6]{
+\newcommand{\image}[4][0.6]{
   % 1 - path to asset
@@
     \includegraphics[width=1.0\textwidth,height=#1\textwidth,keepaspectratio]{#2}
-    \caption[(details)]{\textbf{#4}. #5}
-    \label{fig:#3}
+    \begin{center}
+      \caption[(details)]{\textbf{#4}}
+    \end{center}
+    \vspace{-2em}
+    \label{fig:#2}
   \end{figure}}
@@
 
+\begin{multicols*}{2}
 \section{Introduction}
 
-In the United States, politics has increasingly become a point of conversation due to change of presidency and new bills being signed into laws.
+In the United States, politics has increasingly become a point of conversation due to change in presidency and new, controversial bills being signed into law.
 Cosponsorship provides a rich network between legislators that can be used to explain the political effects and efficiency of legislative processes.
@@
 We first obtained cosponsorship data for the countries: Austria, Denmark, France, Sweden, Switzerland, United Kingdom, and the United States.
-This was taken taken from the following resources: \underline{Bill cosponshorship} \cite{briatte}, \underline{Cosponsorship Network} \cite{fowler}, \underline{UK Parliament} \cite{UK}, and \underline{US Congress} \cite{US}.
+The European networks were produced by a French researcher's website \cite{briatte}.
+The United Kingdom Parliament was scraped from Early Day Motions \cite{UK}, a web portal listing bills discussed.
+The United States Congress data was scraped using a public domain tool \cite{US}.
 The raw data was parsed and saved as \texttt{graphml} files.
-Because the data from many databases were divided based on years, we also had to load and combine various \texttt{graphml} files to create a single network for each country we were analyzing.
+% Because the data from many databases were divided based on years, we also had to load and combine various \texttt{graphml} files to create a single network for each country we were analyzing.
 The data is stored in \texttt{CSE-416-Final-Project/data/} and the pre-processing was performed in the \texttt{Analysis} file in the root directory within our repository.
-
-%TODO: scraping
 
@@
 \subsection{Country-level Results}
-\begin{itemize}
-  \item Every country we look at has some sort of temporal data except for Denmark and the UK.
-Explain why we don't have the data because of how the database worked.
-But we still performed the same summary statistics and produced graphs.
-  \item Austria - the number of edges and vertices do not fluctuate between the years for most countries.
-Number of vertices around 63.
-Average degree has been relatively stable, which is expected given the lack of change in edges and vertices.
-Excess degree decreases from 1995 to 1999.
-The excess degree dropped to around 2, which is similar to the average degree for Austria.
+We will now go through the summary results for each country observed.
+It is important to note that every country we collected data on had temporal data except for Denmark and the UK, which was a product of the resource from which we obtained the data.
+However, we still produced the same summary statistics and produced graphs whenever possible.
+
+For Austria, the number of vertices and edges did not fluctuate between the years, maintaining average values of 63.1 and 63.0, respectively.
+As expected from this result, average degree has also been relatively stable.
+Excess degree decreased dramatically from 1995 to 1999, dropping from 4.5 to 2, which is similar to the average degree.
 This happens to coincide with Austria joining the European Union in 1995.
-It is unclear whether there is a correlation between joining the EU and the sharp decrease in average excess degree.
-However, it can be noted that the drop in excess degrees leads to a similar value as the average degree, which means that the degree of individuals are roughly the same as the degree of their neighbors on average.
-This also means there is less or almost no hub behavior.
-  % To-do: clustering coefficient is 0 for years 94-95, 06-08, 13-18 but we don't know why -- show plots
-  \item France has had a steady increase of vertices.
-It started with a little less than 300 verticies in 1986-1988, and now it is around 500.
-Its number of edges peaked during 2002-2007 to 16,000 from 1986-1988 which had 2,000 edges.
-(During the same time, the clustering coefficient has increased by 1/3.) The average distance has not decreased by much, which is surprising given the amount of increase in vertices.
-  % To-do: figure out what clustering coefficient means
-  \item UK - Number of averages vertices (675) is greater than the average number of edges (663).
-This means that in general, a node has slightly less than one connection.
-The average excess degree is greater than 200, which is greater than 100 times the average degree, which is roughly 2.0.
-This can also be explained when observing a subset of the betweenness graph of UK.
+Although it is unclear whether there is a correlation between these two events, it can be noted that the drop in excess degree close to average degree means that the degree of individuals are roughly the same as their neighbors.
+This also means there is less or vitually no hub behavior.
+
+The France legislative bodies have had a steady increase of vertices, starting with less than 300 certices in 1986 and currently at 500.
+The number of edges peaked during 2002-2007 when it was 16,000.
+The average distance has not decreased by much, which is surprising given the amount of increase in vertices.
+
+For the UK data, the average vertices is around 675, which is greater than the average number of edges (663).
+This means that generally, each node has slightly less than one edge.
+The average excess degree is greater than 200, which is more than 100 times the average degree.
+This can also be explained when observing a subset of the betweenness graph, as seen in Figure \ref{fig:uk-betweenness}.
 The majority of the UK betweenness graph has a single node that is connected to many other nodes that only has one edge.
-  \image[0.2]{Images/uk-betweenness.png}{}{}{}
-  \item Denmark - there are 2 themes that have the most number of vertices, which are economy and justice.
+
+\begin{center}
+  \image[0.2]{Images/uk-betweenness.png}{uk-betweenness}{Subset of UK Betweenness Graph}
+\end{center}
+
+In Denmark, there are two categories that highest number of vertices: economy and justice.
 According to Forbes in December 2017, Denmark is known for its extremely efficient economy and equitable distribution of income.
 It is also currently undergoing an economic expansion.
-Denmark is also rated \#1 for least corruption \cite{denmark}.
-Given this information, it is expected that Denmark would have the most legislators responsible for Economy and Justice.
-  \item Switzerland - there exists few changes in Switzerland's graph statistics over the years.
+Denmark is rated \#1 for least corruption \cite{denmark}.
+Given this information, it is not surprising that Denmark would have the most legislators responsible for Economy and Justice.
+
+There exists few changes in Switzerland's graph statistics over the years.
 The country's clustering coefficient remains consistently around 0.5, and its number of vertices around 130 and its number of edges around 1750.
-  \item Sweden - there is an interesting change in the number of cosponsorships across parties between the years 2014-2018.
+
+There is an interesting change in the number of cosponsorships across Swedish parties between the years 2014-2018.
 The number of vertices across years consistently hover around 350, whereas the number of edges dropped from 4000 in 1988-1991 to 2000 in 2014-2018.
@@
 This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018.
+
 \image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{}{}{}
 \image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{}{}{}
-  \item US - The US had extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (roughly 400).
+
+The US has extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (roughly 400).
 This shows that although members change every 2 years, the legislators and their interactions are relatively stable.
-\end{itemize}
 
 \subsection{Across-Country Results}
-\begin{itemize}
-  \item Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but one of the smallest number of edges (large number of people but very few connections made between them in comparison to other countries)
-  \item Average Degree: US has average degree which is much higher than the average degree for other countries (each node is very highly connected to many other nodes)
-  \item Comparison of Average Degree and Average Excess Degree: UK has one of the lowest average degrees but has the second largest average excess degree.
+
+Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that there are many people with few connections when compared to that of other countries.
+
+Comparison of Average Degree and Average Excess Degree: US has an average degree that is much higher than that of other countries, which is unsurprising given the size of each house and congress.
+The UK also has one of the lowest average degrees but has the second largest average excess degree.
 This means that although each node is not connected to many other nodes, it is on average connected to other important nodes.
 This is a contrast between US and Denmark where their average degree and average excess degrees are relatively similar.
-  \item Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to other countries but has the second smallest average distance (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
+
+Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to that of other countries, but has the second smallest average distance.
+This is expected since legislators are highly connected so the distances between any random two people   (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
+
+\begin{itemize}
+  \item Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to that of other countries, but has the second smallest average distance (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
   \item Comparison of Size of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US nodes are very highly connected and only has a few connected components).
@@
 So this is about 67\%.
+  %To-do check if this is really true because kind of unclear
+  \item Assortativity measures are most positive for  Sweden (around 0.8) and most negative for Austria (around -0.45).
+Positive assortativity measures means that nodes tend to associate more with nodes with similar attributes, while negative assortativity means that nodes associate with nodes with different attributes.
+The US assortativity value is very close to 0, which indicates that there is no preference in either direction.
+  %To-do check US database
+  \image[0.3]{../plots/assortativity/all_countries.png}{}{}{}
 \end{itemize}
@@
 The dynamic social relationships between legislators - of forging new relationships and maintaining older established relationships - matter.
-We have uncovered some intriguing results. First, we notice that the average distance tends to increase as the world gets smaller.
-
-there exists an inverse relationship between the size of a graph and its average distance.
+Moreover, our generated outputs hints at past and ongoing events that impact legislative cosponsorships.
+For example, the drop in number of cosponsorships across different parties in 2014-2018 in Sweden reflects the events that unfolded during the 2014 general elections,
+We have uncovered some intriguing results.
+First, we notice that the average distance tends to increase as the world gets smaller.
+One interpretation of this result is that members tend to be more isolated and fewer are willing to cooporate outside of their local network.
+As the world gets larger, the friendship circles that define and maintain social relationships grow.
+As communication between legislators improves, links become increasingly more interconnected, and the relative distance between any two given legislators decreases.
+This underlying phenomenom is reflected in the comparison of clustering coefficients across countries.
+For example, small countries like Austria or Denmark have low clustering coefficients of 0 and 0.2 respectively, whereas a large country like the US has a clustering coefficient of nearly 1.
+We also notice a surprising outcome in the US assortativity graph.
+We expected partisanship between the democratic and republican party.
+However, the US graphs have an assortativity of around 0, which suggests that there exists much more bipartisanship than one would think.
 
@@
 
+\end{multicols*}
 \end{document}

### 2018-12-11 paper/paper.tex
paper

@@
     \end{center}
+    \label{fig:#3}
     \vspace{-2em}
-    \label{fig:#2}
   \end{figure}}
@@
 
-In Denmark, there are two categories that highest number of vertices: economy and justice.
+In Denmark, there are two categories that highest number of vertices: Economy and Justice.
 According to Forbes in December 2017, Denmark is known for its extremely efficient economy and equitable distribution of income.
@@
 Denmark is rated \#1 for least corruption \cite{denmark}.
-Given this information, it is not surprising that Denmark would have the most legislators responsible for Economy and Justice.
+Given this information, it is not surprising that Denmark would have the most legislators assigned to Economy and Justice.
 
-There exists few changes in Switzerland's graph statistics over the years.
-The country's clustering coefficient remains consistently around 0.5, and its number of vertices around 130 and its number of edges around 1750.
+There exists few changes in Switzerland's graph statistics over the years observed.
+The country's clustering coefficient remains consistently around 0.5, its number of vertices around 130, and its number of edges around 1750.
+According to BBC, Switzerland's neutrality and political stability has allowed it to become one of the world's wealthiest countries \cite{switzerland}.
+This knowledge helps explain why Switzerland's legislative data has barely changed over the last decade.
 
@@
 
-Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that there are many people with few connections when compared to that of other countries.
+Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.
 
-Comparison of Average Degree and Average Excess Degree: US has an average degree that is much higher than that of other countries, which is unsurprising given the size of each house and congress.
+Comparison of Average Degree and Average Excess Degree: US has an average degree that is much higher than that of other countries, which is unsurprising given the sheer size of each house and congress.
 The UK also has one of the lowest average degrees but has the second largest average excess degree.
@@
 Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to that of other countries, but has the second smallest average distance.
-This is expected since legislators are highly connected so the distances between any random two people   (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
+This is expected since legislators are highly connected so the distances between any random two people is much less when compared to other countries.
 
-\begin{itemize}
-  \item Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to that of other countries, but has the second smallest average distance (there are many nodes but they are very highly connected so the distance between any two random nodes is much less than other countries)
-  \item Comparison of Size of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US nodes are very highly connected and only has a few connected components).
+Comparison of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US nodes are very highly connected with only a few connected components).
 In comparison, France has an average size of LCC that is slightly lower than the average of all countries, but it has the highest number of CC.
-  \item US graph is almost completely connected.
-Fully connected graphs have $n(n-1)/2$ edges.
-There are about 100,000 edges and 552 vertices.
-A complete graph would have 152,076.
-So this is about 67\%.
+
+US graph is almost completely connected. Fully connected graphs have $n(n-1)/2$ edges. There are about 100,000 edges and 552 vertices. A complete graph would have 152,076. So this is about 67\%.
 %To-do check if this is really true because kind of unclear
-  \item Assortativity measures are most positive for  Sweden (around 0.8) and most negative for Austria (around -0.45).
+
+Assortativity measures are most positive for Sweden (around 0.8) and most negative for Austria (around -0.45).
 Positive assortativity measures means that nodes tend to associate more with nodes with similar attributes, while negative assortativity means that nodes associate with nodes with different attributes.
 The US assortativity value is very close to 0, which indicates that there is no preference in either direction.
+
 %To-do check US database
 \image[0.3]{../plots/assortativity/all_countries.png}{}{}{}
-\end{itemize}
 
@@
 For example, small countries like Austria or Denmark have low clustering coefficients of 0 and 0.2 respectively, whereas a large country like the US has a clustering coefficient of nearly 1.
-We also notice a surprising outcome in the US assortativity graph.
+We also notice a outcome in the US assortativity graph.
 We expected partisanship between the democratic and republican party.
@@
 
-\newpage
 \begin{thebibliography}{9}
@@
 
+\bibitem{switzerland} ``Switzerland country profile.'' \emph{BBC News}, BBC, 22 May 2018. \url{https://www.bbc.com/news/world-europe-17980650}
+
 \bibitem{UK} UK Parliament. \url{https://edm.parliament.uk/}

### 2018-12-11 lib/analysis/stats.py
fix us graphs;

@@ -1,20 +1,16 @@
 import graph_tool.all as gt
 import numpy as np
+import pandas as pd
 from functools import reduce
 from .clustering import coefficient as clustering_coefficient
 from .dist import degree, excess_degree
 
-def generate_party_property(g: gt.Graph, label: str):
-    partyMap = {}
-    out = []
-    parties = [party for party in g.vertex_properties[label]]
-    d = dict([(y,x+1) for x,y in enumerate(sorted(set(parties)))])
-    for party in parties:
-        out.append(d[party])
-    party_id = g.new_vertex_property("int32_t")
-    for i in range(len(out)):
-        party_id[g.vertex(i)] = out[i]
-    g.vertex_properties['party_id'] = party_id
+def generate_party_property(g: gt.Graph, label='party'):
+    party_map = pd.Series(list(g.vp[label]))
+    enum_map = {party: i for i, party in enumerate(party_map.unique())}
+    party_id = party_map.replace(enum_map).values
+    g.vp['party_id'] = g.new_vp('int', party_id)
+    return g.vp['party_id'] 
 
 def assortativity(g: gt.Graph, attribute_map: gt.PropertyMap) -> np.float:
     coeff, _ = gt.assortativity(g, attribute_map)

### 2018-12-11 lib/scrape/us_extract_legislator_info.py

@@ -1,37 +1,25 @@
 import os
 import json
+from functools import reduce
 
 path = '../../data/us/raw/legislators'
-sessions = ['113', '114', '115']
-dates = {
-    '113': (2013,2015),
-    '114': (2015,2017),
-    '115': (2017,2019)
-}
-
-def in_session(session, term):
-    start, end = dates[session]
-    tstart, tend = int(term["start"][:4]), int(term["end"][:4])
-    return tstart <= start and end <= tend
-
 legislators = {}
 
 for file in ['legislators-current.json', 'legislators-historical.json']:
     with open(os.path.join(path, file), 'r') as f:
         data = json.load(f)
-        for session in sessions:
-            for member in data:
-                id_ = member['id']['bioguide']
-                for term in member['terms']:
-                    if '2013' <= term['start'][:4]:
-                        if session not in legislators:
-                            legislators[session] = {}
-                        if id_ not in legislators[session]:
-                            legislators[session][id_] = term['party']
+        for member in data:
+            id_ = member['id']['bioguide']
+            if id_ not in legislators:
+                legislators[id_] = member['terms']                
 
-
-for session in sessions:
-    with open(f'{path}/parties.{session}.csv', 'w+') as f:
-        f.write('bioguide_id,party\n')
-        for id_, party in legislators[session].items():
-            f.write(f'{id_},{party}\n')
+with open(f'{path}/terms.csv', 'w') as f:
+    f.write('bioguide_id,party\n')
+    for id_, terms in legislators.items():
+        parties = []
+        for i, term in enumerate(terms):
+            if int(term['end'][:4]) >= 2013 or int(term['start'][:4]) >= 2013:
+                party = term['party'] if 'party' in term else 'Independent'
+                parties.append(party)
+        if int(term['end'][:4]) >= 2013 or int(term['start'][:4]) >= 2013:
+            f.write(f'{id_},{parties[-1]}\n')

### 2018-12-11 paper/paper.tex
updating paper

@@
 This result happens to coincide with an event during the 2014 Swedish general election, in which the Social Democrats declared that they would not work with the Sweden Democrats.
-This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018.
+This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018, seen in Figure \ref{fig:swe_ass_1988} and \ref{fig:swe_ass_2014}.
 
-\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{}{}{}
-\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{}{}{}
+\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{swe_ass_1988}{Sweden Assortativity 1988-1991}
+\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{swe_ass_2014}{Sweden Assortativity 2014-2018}
 
@@
 
+% TO DO:
+%---------------------------------------------------------------------------
 Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.
@@
 
+% ------------------------------------------------------------------------
+
 \section{Discussion}
@@
 For example, small countries like Austria or Denmark have low clustering coefficients of 0 and 0.2 respectively, whereas a large country like the US has a clustering coefficient of nearly 1.
-We also notice a outcome in the US assortativity graph.
-We expected partisanship between the democratic and republican party.
-However, the US graphs have an assortativity of around 0, which suggests that there exists much more bipartisanship than one would think.
+We also notice extreme partisanship in the US senate, which is expected given the party division between the Republicans and Democrats, and reflect
+
+Gordon Ramsay: "This SOUp, IS DRY!!!"
 

### 2018-12-11 paper/paper.tex
fixed figure labeling
changes

@@
 In comparison, France has an average size of LCC that is slightly lower than the average of all countries, but it has the highest number of CC.
+We also observe that the generated graphs reflect the underlying structure of governance.
+For example, f assortativity
+%assortativity_net_fr_an2012-2017.pdf
 
@@
 %To-do check US database
-\image[0.3]{../plots/assortativity/all_countries.png}{}{}{}
+\image[0.3]{../plots/assortativity/all_countries.pdf}{}{}
 
@@
 For example, small countries like Austria or Denmark have low clustering coefficients of 0 and 0.2 respectively, whereas a large country like the US has a clustering coefficient of nearly 1.
-We also notice extreme partisanship in the US senate, which is expected given the party division between the Republicans and Democrats, and reflect
+We also notice extreme partisanship in the US senate, which is expected given the party division and clashes between the Republicans and Democrats.
 

### 2018-12-11 paper/paper.tex
edits to paper and across-country plot

@@
 \usepackage{graphicx}                  % for figures
+\usepackage{grffile}
 \usepackage{amsmath}                   % for extented math markup
@@
     \begin{center}
-      \caption[(details)]{\textbf{#4}}
+      \caption[(details)]{\textbf{#4}\label{fig:#3}}
     \end{center}
-    \label{fig:#3}
     \vspace{-2em}
@@
 
-\title{Comparative Analysis of Legislative Complex Networks of Select North American and European Countries}
+\title{Comparative Analysis of Legislative Complex Networks}
 \author{\names \\ \small\url{https://github.com/jowch/CSE-416-Final-Project}}
@@
 
-\section{Results}
+\section{Results and Discussion}
 \subsection{Country-level Results}
 We will now go through the summary results for each country observed.
-It is important to note that every country we collected data on had temporal data except for Denmark and the UK, which was a product of the resource from which we obtained the data.
+It is important to note that every country we collected data on had temporal data except for Denmark and the UK, which was due to the structure of the resource from which we obtained the data.
 However, we still produced the same summary statistics and produced graphs whenever possible.
@@
 Although it is unclear whether there is a correlation between these two events, it can be noted that the drop in excess degree close to average degree means that the degree of individuals are roughly the same as their neighbors.
-This also means there is less or vitually no hub behavior.
+This means that there was, on average, a sharp decrease in hub behavior to nearly none at all.
 
-The France legislative bodies have had a steady increase of vertices, starting with less than 300 certices in 1986 and currently at 500.
+The France legislative bodies have had a steady increase of vertices, starting with less than 300 vertices in 1986 to 500 today.
 The number of edges peaked during 2002-2007 when it was 16,000.
 The average distance has not decreased by much, which is surprising given the amount of increase in vertices.
+
+There exists few changes in Switzerland's graph statistics over the years observed.
+The country's clustering coefficient remains consistently around 0.5, its number of vertices around 130, and its number of edges around 1750.
+According to BBC, Switzerland's neutrality and political stability has allowed it to become one of the world's wealthiest countries \cite{switzerland}.
+This knowledge helps explain why Switzerland's legislative data has barely changed over the last decade.
+
+There is an interesting change in the number of cosponsorships across Swedish parties between the years 2014-2018.
+The number of vertices across years consistently hover around 350, whereas the number of edges dropped from 4000 in 1988-1991 to 2000 in 2014-2018.
+This result happens to coincide with an event during the 2014 Swedish general election, in which the Social Democrats declared that they would not work with the Swedish Democrats.
+This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018, seen in Figures \ref{fig:swe_ass_1988} and \ref{fig:swe_ass_2014}
+
+\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{swe_ass_1988}{Sweden Assortativity 1988-1991}
+\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{swe_ass_2014}{Sweden Assortativity 2014-2018}
+
+The US has extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (roughly 400).
+This shows that although members change every 2 years, the legislators and their interactions are relatively stable.
+Most notably, the United States legislative bodies have highest completeness (67\%; Figure \ref{fig:completeness}) amongst the examined graphs, where completeness is the ratio between the number of edges in a graph and the number of edges in a complete graph with the same number of vertices.
+
+\image[0.3]{../plots/averages/completeness.pdf}{completeness}{Graph Completeness}
 
@@
 
-There exists few changes in Switzerland's graph statistics over the years observed.
-The country's clustering coefficient remains consistently around 0.5, its number of vertices around 130, and its number of edges around 1750.
-According to BBC, Switzerland's neutrality and political stability has allowed it to become one of the world's wealthiest countries \cite{switzerland}.
-This knowledge helps explain why Switzerland's legislative data has barely changed over the last decade.
-
-There is an interesting change in the number of cosponsorships across Swedish parties between the years 2014-2018.
-The number of vertices across years consistently hover around 350, whereas the number of edges dropped from 4000 in 1988-1991 to 2000 in 2014-2018.
-This result happens to coincide with an event during the 2014 Swedish general election, in which the Social Democrats declared that they would not work with the Sweden Democrats.
-This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018, seen in Figure \ref{fig:swe_ass_1988} and \ref{fig:swe_ass_2014}.
-
-\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{swe_ass_1988}{Sweden Assortativity 1988-1991}
-\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{swe_ass_2014}{Sweden Assortativity 2014-2018}
-
-The US has extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (roughly 400).
-This shows that although members change every 2 years, the legislators and their interactions are relatively stable.
-
 \subsection{Across-Country Results}
 
-% TO DO:
+% TODO:
 %---------------------------------------------------------------------------
-Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.
 
-Comparison of Average Degree and Average Excess Degree: US has an average degree that is much higher than that of other countries, which is unsurprising given the sheer size of each house and congress.
+We seek now to compare our results between countries.
+We see that, when comparing the number of edges and number of vertices, the UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.
+This can be observed in Figure \ref{fig:edge-vert}.
+\image[0.26]{../plots/across-country/Number of EdgesNumber of Vertices}{edge-vert}{Number of Edges and Vertices}
+However, the UK has the second largest average excess degree, which means that although each legislator is not connected to many others, they are on average connected to other relatively important individuals.
+On the other hand, the US has an average degree that is much higher than that of other countries.
+We notice that the graph structure of the US - much like that of the UK - is separated into clumps.
+But unlike the UK, the US depicts an extreme partisonship structure \ref{fig:us_ass}, \ref{fig:uk_ass}.
+
+\image[0.3]{../plots/graph/US/assortativity/assortativity_us.115.pdf}{us_ass}{US Assortativity 115}
+\image[0.3]{../plots/graph/UK/assortativity/assortativity_uk.pdf}{uk_ass}{UK Assortativity}
+
+When compared to other countries, the US has a much larger average number of edges, and has the second smallest average distance.
+These results are not surprising, since legislators in the US are highly connected, so the distances between any random two people in the same clumps is much less compared to that of other country.
+We also observe that the generated graphs reflect the underlying structure of governance.
+For example, from Figure \ref{fig:fr_assortativity} we notice that the pink component has a single central actor, and one can thus make an educated guess that the cluster represents the French Socialist Party.
+
+\image[0.3]{../plots/graph/france/assortativity/assortativity_net_fr_an2012-2017.pdf}{fr_assortativity}{France Assortativity 2012-2017}
+
+% Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.
+
+% Comparison of Average Degree and Average Excess Degree: US has an average degree that is much higher than that of other countries, which is unsurprising given the sheer size of each house and congress.
 The UK also has one of the lowest average degrees but has the second largest average excess degree.
@@
 
-Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to that of other countries, but has the second smallest average distance.
+% Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to that of other countries, but has the second smallest average distance.
 This is expected since legislators are highly connected so the distances between any random two people is much less when compared to other countries.
 
-Comparison of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US nodes are very highly connected with only a few connected components).
+% Comparison of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US nodes are very highly connected with only a few connected components).
 In comparison, France has an average size of LCC that is slightly lower than the average of all countries, but it has the highest number of CC.
 We also observe that the generated graphs reflect the underlying structure of governance.
-For example, f assortativity
-%assortativity_net_fr_an2012-2017.pdf
+For example, from Figure \ref{fig:fr_assortativity} we notice that the pink component represents the French Socialist Party, with one central actor in the middle.
+% \image[0.3]{../plots/graph/france/assortativity/assortativity_net_fr_an2012-2017.pdf}{fr_assortativity}{France Assortativity 2012-2017}
 
@@
 
-Assortativity measures are most positive for Sweden (around 0.8) and most negative for Austria (around -0.45).
+Assortativity measures can be seen in Figure \ref{fig:ass}.
+Assortativity values are most positive for Sweden (around 0.8) and most negative for Austria (around -0.45).
 Positive assortativity measures means that nodes tend to associate more with nodes with similar attributes, while negative assortativity means that nodes associate with nodes with different attributes.
@@
 %To-do check US database
-\image[0.3]{../plots/assortativity/all_countries.pdf}{}{}
+\image[0.3]{../plots/assortativity/all_countries.pdf}{ass}{All-Country Assortativity Measures}
 
@@
 Moreover, our generated outputs hints at past and ongoing events that impact legislative cosponsorships.
-For example, the drop in number of cosponsorships across different parties in 2014-2018 in Sweden reflects the events that unfolded during the 2014 general elections,
+For example, the drop in number of cosponsorships across different parties in 2014-2018 in Sweden reflects the events that unfolded during the 2014 general elections.
 We have uncovered some intriguing results.
@@
 We also notice extreme partisanship in the US senate, which is expected given the party division and clashes between the Republicans and Democrats.
+The two components of the graph also represent the house and the senate.
+The house and the senate differ from an institutional design and have contrasting social structures, and so we would expect the behaviour in these two components to exhibit unique characteristics as well.
+Although we did not conduct any direct tests, the house and senate should differ in quantities such as clustering coefficient and average path length.
 
-Gordon Ramsay: "This SOUp, IS DRY!!!"
+Gordon Ramsay: ``ThIs SoUp, Is DrY!!!''
 

### 2018-12-11 paper/paper.tex
updated paper

@@
     \end{center}
-    \vspace{-2em}
+    \vspace{-3em}
   \end{figure}}
@@
 
-In Denmark, there are two categories that highest number of vertices: Economy and Justice.
+In Denmark, there are two categories that have the highest number of vertices: Economy and Justice.
 According to Forbes in December 2017, Denmark is known for its extremely efficient economy and equitable distribution of income.
@@
 We notice that the graph structure of the US - much like that of the UK - is separated into clumps.
-But unlike the UK, the US depicts an extreme partisonship structure \ref{fig:us_ass}, \ref{fig:uk_ass}.
+But unlike the UK, the US depicts an extreme partisonship structure in Figure \ref{fig:us_ass}, and Figure \ref{fig:uk_ass}.
 
@@
 When compared to other countries, the US has a much larger average number of edges, and has the second smallest average distance.
-These results are not surprising, since legislators in the US are highly connected, so the distances between any random two people in the same clumps is much less compared to that of other country.
+These results are not surprising, since legislators in the US are highly connected, so the distances between any random two people in the same clumps are much less compared to that of other country.
 We also observe that the generated graphs reflect the underlying structure of governance.
@@
 
-% Comparison of Number of Edges and Number of Vertices: UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.
-
-% Comparison of Average Degree and Average Excess Degree: US has an average degree that is much higher than that of other countries, which is unsurprising given the sheer size of each house and congress.
-The UK also has one of the lowest average degrees but has the second largest average excess degree.
-This means that although each node is not connected to many other nodes, it is on average connected to other important nodes.
-This is a contrast between US and Denmark where their average degree and average excess degrees are relatively similar.
-
-% Comparison of Number of Edges and Average Distance: US has a much larger average number of edges when compared to that of other countries, but has the second smallest average distance.
-This is expected since legislators are highly connected so the distances between any random two people is much less when compared to other countries.
-
-% Comparison of LCC and Number of CC: US has the largest average size of LCC but has the smallest number of CC (US nodes are very highly connected with only a few connected components).
-In comparison, France has an average size of LCC that is slightly lower than the average of all countries, but it has the highest number of CC.
-We also observe that the generated graphs reflect the underlying structure of governance.
-For example, from Figure \ref{fig:fr_assortativity} we notice that the pink component represents the French Socialist Party, with one central actor in the middle.
-% \image[0.3]{../plots/graph/france/assortativity/assortativity_net_fr_an2012-2017.pdf}{fr_assortativity}{France Assortativity 2012-2017}
-
-US graph is almost completely connected. Fully connected graphs have $n(n-1)/2$ edges. There are about 100,000 edges and 552 vertices. A complete graph would have 152,076. So this is about 67\%.
+% US graph is almost completely connected. Fully connected graphs have $n(n-1)/2$ edges. There are about 100,000 edges and 552 vertices. A complete graph would have 152,076. So this is about 67\%.
 %To-do check if this is really true because kind of unclear
@@
 \image[0.3]{../plots/assortativity/all_countries.pdf}{ass}{All-Country Assortativity Measures}
+
+We also expect that each country should exhibit power-law distributions, as there should exist hubs of legislative members with very high degree centralities.
+This turns out to be the case for smaller less densley connected graphs such as Sweden in Figure \ref{fig:se_deg}.
+However, this does not hold true for largely connected graphs such as the US, as seen in Figure \ref{fig:us_deg}.
+The US graph is almost a completely connected graph; Fully connected graphs have $n(n-1)/2$ edges.
+There are roughly 100,000 edges and 552 vertices in our US graph.
+In this case a complete graph would have 152,076, so the US is about 67\% of a fully connected graph.
+
+\image[0.3]{../plots/distributions/sweden/degree/degree_net_se2014-2018.graphml.png}{se_deg}{Sweden Degree Distribution 2014-2018}
+\image[0.3]{../plots/distributions/us/degree/degree_us.115.graphml.png}{us_deg}{US Degree Distribution 115}
 
@@
 Although we did not conduct any direct tests, the house and senate should differ in quantities such as clustering coefficient and average path length.
-
-Gordon Ramsay: ``ThIs SoUp, Is DrY!!!''
+Lastly, we examined the degree distributions of every graph, and expected that they follow power-law distributions. As it turns out, this does not hold true for large densley connected graphs.
 

### 2018-12-11 paper/paper.tex
updated paper

@@
     \end{center}
-    \vspace{-3em}
+    \vspace{-2.5em}
   \end{figure}}
@@
 
-According a study conducted by James Folwer from the Department of Political Science at the University of California, Davis, there are several trends that have been observed among legislators.
+According to a study conducted by James Folwer from the Department of Political Science at the University of California, Davis, there are several trends that have been observed among legislators.
 In the United States, biennial elections cause members of the U.S.
@@
 
-The US has extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (roughly 400).
+The US has an extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (roughly 400).
 This shows that although members change every 2 years, the legislators and their interactions are relatively stable.
@@
 On the other hand, the US has an average degree that is much higher than that of other countries.
-We notice that the graph structure of the US - much like that of the UK - is separated into clumps.
-But unlike the UK, the US depicts an extreme partisonship structure in Figure \ref{fig:us_ass}, and Figure \ref{fig:uk_ass}.
+This can be seen in the Figure \ref{fig:degree-excess}
+\image[0.26]{../plots/across-country/Average DegreeAverage Excess Degree.pdf}{degree-excess}{Average Degree and Excess Degree}
+We notice that the graph structure of the US - much like that of the UK - is separated into clumps. But unlike the UK, the US depicts an extreme partisonship structure in Figure \ref{fig:us_ass}.
 
@@
 We also observe that the generated graphs reflect the underlying structure of governance.
-For example, from Figure \ref{fig:fr_assortativity} we notice that the pink component has a single central actor, and one can thus make an educated guess that the cluster represents the French Socialist Party.
+For example, from the France graph in Figure \ref{fig:fr_assortativity} we notice that the pink component has a single central actor, and one can thus make an educated guess that the cluster represents the French Socialist Party.
 
@@
 \section{Discussion}
+\begin{itemize}
+  \item Stability over time: US and France, something about democracy
+  \item US - Has very consistent statistics.
+While the number of vertices do not change every two years during the turnaround, the number of edges do not necessarily need to be the same.
+However, the trend that the number of edges does not fluctuate widely across the years suggests that it is possible that the process that the legislators undergo is very stable and potentially inflexible.
+This is not innately a negative or positive trait of the United States legislative system
+  \item France - steady increase in vertices but average distance does not change.
+This could imply that new members when they join the Parliament are joining existing neighborhoods rather than building new bridges.
+This could suggest that there is a strong party identity in France.
+\end{itemize}
 For our project, we use legislative cosponsorship networks across the US and selected European countries to try to infer social relationships in government that may influence legislative behavior.

### 2018-12-11 paper/paper.tex
paper done

--- 2018-12-11 paper/paper.tex
@@
 \usepackage{multicol}
+\usepackage{titlesec}
+\usepackage{subcaption}
 
@@
 
+\titleformat*{\section}{\large\bfseries}
+\titleformat*{\subsection}{\normalsize\bfseries}
+
 % environment for cases
@@
 \captionsetup[figure]{
+  font={singlespacing},
+  labelfont=bf,
+  singlelinecheck=off,
+  justification=centering,
+  labelsep=period
+}
+
+\captionsetup[subfigure]{
   font={footnotesize,singlespacing},
@@
   singlelinecheck=off,
-  justification=raggedright,
-  labelsep=period
+  justification=centering
 }
 
-\newcommand{\image}[4][0.6]{
-  % 1 - path to asset
-  % 2 - label
-  % 3 - title
-  % 4 - caption
-  \begin{figure}[H]
+\newcommand{\doubleimage}[7]{
+  % 1 - figure title
+  % 2 - path to asset 1
+  % 3 - label
+  % 4 - title
+  % 5 - path to asset 2
+  % 6 - label
+  % 7 - title
+  \begin{figure*}[t]
     \centering
-    \includegraphics[width=1.0\textwidth,height=#1\textwidth,keepaspectratio]{#2}
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=0.8\textwidth,height=0.5\textwidth,keepaspectratio]{#2}
+      \caption[(details)]{\textbf{#4}\label{fig:#3}}
+    \end{subfigure}%
+    \begin{subfigure}{.5\textwidth}
+      \centering
+      \includegraphics[width=0.8\textwidth,height=0.5\textwidth,keepaspectratio]{#5}
+      \caption[(details)]{\textbf{#7}\label{fig:#6}}
+    \end{subfigure}
     \begin{center}
-      \caption[(details)]{\textbf{#4}\label{fig:#3}}
+      \caption{\textbf{#1}}
     \end{center}
-    \vspace{-3em}
-  \end{figure}}
+    \vspace{-2em}
+  \end{figure*}
+}
 
@@
                    escapeinside=||,mathescape,python3}
+
+\newcommand{\code}[1]{\small\texttt{#1}}
 
@@
 
-\date{December 11, 2018}
+\date{December 12, 2018}
 
 \begin{document}
+% \newgeometry{top=0.5in}  %% I increased for demo
+\vspace{-2em}
 \maketitle
@@
 \thispagestyle{empty}
+% \restoregeometry
 
-\begin{abstract}
-    Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries.
+% \begin{abstract}
+%     Given the complex nature of today's political climate, we were interested in analyzing and quantifying various legislative bodies in select first-world countries.
 To do so, we performed complex network analysis on seven North Amerian and European countries (Austria, Denmark, France, Sweden, Switerland, UK, and US) to understand how a wide variety political parties interacted amongst each other with respect to cosponsorship.
 We found and plotted summary statistics and centrality measures to make comparisons possible.
-\end{abstract}
+% \end{abstract}
 
@@
 \subsection{Data Collection and Pre-Processing}
-We first obtained cosponsorship data for the countries: Austria, Denmark, France, Sweden, Switzerland, United Kingdom, and the United States.
+We obtained cosponsorship data for the countries: Austria, Denmark, France, Sweden, Switzerland, United Kingdom, and the United States.
 The European networks were produced by a French researcher's website \cite{briatte}.
@@
 The United States Congress data was scraped using a public domain tool \cite{US}.
-The raw data was parsed and saved as \texttt{graphml} files.
+The raw data was parsed and saved as \code{graphml} files.
 % Because the data from many databases were divided based on years, we also had to load and combine various \texttt{graphml} files to create a single network for each country we were analyzing.
-The data is stored in \texttt{CSE-416-Final-Project/data/} and the pre-processing was performed in the \texttt{Analysis} file in the root directory within our repository.
+% The data is stored in \code{CSE-416-Final-Project/data/} and the pre-processing was performed in the \code{Analysis} file in the root directory within our repository.
 
@@
 
-Our analysis was performed using a library called \href{https://graph-tool.skewed.de}{graph-tool}, which provides Python bindings to powerful abstractions and parallel algorithms for processing graphs.
+Our analysis was performed using the library \href{https://graph-tool.skewed.de}{graph-tool}, which provides Python bindings to powerful abstractions and parallel algorithms for processing graphs.
 In addition, we used \texttt{numpy}, \texttt{scipy}, \texttt{pandas}, \texttt{seaborn}, and \texttt{matplotlib} to perform the comparative analysis.
@@
 Vertices and edges that are yellow and larger in size reflect greater importance, whilst those that are blue and smaller in size reflect lesser importance.
-For the generated betweenness graphs, the top 3 percent of legislators with the highest betweenness centralities were colored yellow and enlarged.
+For the generated betweenness graphs, the top three percent of legislators with the highest betweenness centralities were colored yellow and enlarged.
 
@@
 We will now go through the summary results for each country observed.
-It is important to note that every country we collected data on had temporal data except for Denmark and the UK, which was due to the structure of the resource from which we obtained the data.
+Every country we collected data on had temporal data except for Denmark and the UK, which was due to the structure of the data resource.
 However, we still produced the same summary statistics and produced graphs whenever possible.
 
-For Austria, the number of vertices and edges did not fluctuate between the years, maintaining average values of 63.1 and 63.0, respectively.
-As expected from this result, average degree has also been relatively stable.
+For Austria, the number of vertices and edges did not fluctuate between the years, and maintained average values of 63.1 and 63.0 respectively.
+As expected, average degree also stayed relatively stable.
 Excess degree decreased dramatically from 1995 to 1999, dropping from 4.5 to 2, which is similar to the average degree.
@@
 Although it is unclear whether there is a correlation between these two events, it can be noted that the drop in excess degree close to average degree means that the degree of individuals are roughly the same as their neighbors.
-This means that there was, on average, a sharp decrease in hub behavior to nearly none at all.
+This means that there was on average a sharp decrease in hub behavior.
 
-The France legislative bodies have had a steady increase of vertices, starting with less than 300 vertices in 1986 to 500 today.
-The number of edges peaked during 2002-2007 when it was 16,000.
-The average distance has not decreased by much, which is surprising given the amount of increase in vertices.
+The French legislative bodies had a steady increase of vertices, starting with less than 300 vertices in 1986 to 500 today.
+The number of edges peaked during 2002-2007 at 16,000.
+The average distance has not decreased dramatically, which is surprising given the increase in vertices.
 
-There exists few changes in Switzerland's graph statistics over the years observed.
-The country's clustering coefficient remains consistently around 0.5, its number of vertices around 130, and its number of edges around 1750.
+Switzerland's graph statistics have been stable over the years observed.
+The country's clustering coefficient remains around 0.5, its number of vertices around 130, and its number of edges around 1750.
 According to BBC, Switzerland's neutrality and political stability has allowed it to become one of the world's wealthiest countries \cite{switzerland}.
@@
 
-There is an interesting change in the number of cosponsorships across Swedish parties between the years 2014-2018.
+There was an interesting change in the number of cosponsorships across Swedish parties between the years 2014-2018.
 The number of vertices across years consistently hover around 350, whereas the number of edges dropped from 4000 in 1988-1991 to 2000 in 2014-2018.
-This result happens to coincide with an event during the 2014 Swedish general election, in which the Social Democrats declared that they would not work with the Swedish Democrats.
-This decrease in edges across parties is evidently seen when comparing the assortativity graphs from the years 1988-1991 and 2014-2018, seen in Figures \ref{fig:swe_ass_1988} and \ref{fig:swe_ass_2014}
+This result happens to coincide with the 2014 Swedish general election, in which the Social Democrats declared that they would not work with the Swedish Democrats.
+This decrease in edges across parties is evident when comparing graphs from the years 1988-1991 and 2014-2018, seen in Figures \ref{fig:swe_ass_1988} and \ref{fig:swe_ass_2014}
 
-\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{swe_ass_1988}{Sweden Assortativity 1988-1991}
-\image[0.3]{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{swe_ass_2014}{Sweden Assortativity 2014-2018}
+\doubleimage
+{}{../plots/graph/sweden/assortativity/assortativity_net_se1988-1991.pdf}{swe_ass_1988}{Sweden Assortativity 1988-1991}{../plots/graph/sweden/assortativity/assortativity_net_se2014-2018.pdf}{swe_ass_2014}{Sweden Assortativity 2014-2018}
 
-The US has extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (roughly 400).
-This shows that although members change every 2 years, the legislators and their interactions are relatively stable.
-Most notably, the United States legislative bodies have highest completeness (67\%; Figure \ref{fig:completeness}) amongst the examined graphs, where completeness is the ratio between the number of edges in a graph and the number of edges in a complete graph with the same number of vertices.
-
-\image[0.3]{../plots/averages/completeness.pdf}{completeness}{Graph Completeness}
+The United States has an extremely consistent number of edges (around 100,000), vertices (a little over 500), clustering coefficient (almost 1.0), average degree (around 350), and average excess degree (around 400).
+This shows that despite changing some members every two years, the legislators and their interactions are relatively stable.
+Most notably, the US legislative bodies have highest completeness (67\%; Figure \ref{fig:completeness}) amongst the examined graphs, where completeness is the ratio between the number of edges in a graph and the number of edges in a complete graph with the same number of vertices.
 
@@
 This can also be explained when observing a subset of the betweenness graph, as seen in Figure \ref{fig:uk-betweenness}.
-The majority of the UK betweenness graph has a single node that is connected to many other nodes that only has one edge.
+The majority of the UK betweenness graph has a single node that is surrounded by many other nodes.
 
-\begin{center}
-  \image[0.2]{Images/uk-betweenness.png}{uk-betweenness}{Subset of UK Betweenness Graph}
-\end{center}
+\doubleimage{}{../plots/averages/completeness.pdf}{completeness}{Graph Completeness}{Images/uk-betweenness.png}{uk-betweenness}{Subset of UK Betweenness Graph}
 
@@
 
-% TODO:
-%---------------------------------------------------------------------------
+The next step to our analysis is to compare results between countries.
+When comparing the average number of edges and vertices for each country, the UK has the largest number of vertices but the fewest number of edges, signifying that the country has a very low average degree.
+This property can be observed in Figure \ref{fig:edge-vert}.
 
-We seek now to compare our results between countries.
-We see that, when comparing the number of edges and number of vertices, the UK has the largest number of vertices but the fewest number of edges, which means that the country has a very low average degree since there are many people with few connections when compared to that of other countries.
-This can be observed in Figure \ref{fig:edge-vert}.
-\image[0.26]{../plots/across-country/Number of EdgesNumber of Vertices}{edge-vert}{Number of Edges and Vertices}
-However, the UK has the second largest average excess degree, which means that although each legislator is not connected to many others, they are on average connected to other relatively important individuals.
-On the other hand, the US has an average degree that is much higher than that of other countries.
-We notice that the graph structure of the US - much like that of the UK - is separated into clumps.
-But unlike the UK, the US depicts an extreme partisonship structure in Figure \ref{fig:us_ass}, and Figure \ref{fig:uk_ass}.
+However, we can also compare the average degree and excess degree across countries.
+Despite the low average degree, the UK also has the second largest average excess degree.
+This means that although each vertex is not connected to many other vertices, they are on average connected to relatively important individuals.
+On the other hand, the US has the highest average degree and the highest average excess degree.
+This can be observed in the Figure \ref{fig:degree-excess}
 
-\image[0.3]{../plots/graph/US/assortativity/assortativity_us.115.pdf}{us_ass}{US Assortativity 115}
-\image[0.3]{../plots/graph/UK/assortativity/assortativity_uk.pdf}{uk_ass}{UK Assortativity}
+\doubleimage{}{../plots/across-country/Number of EdgesNumber of Vertices}{edge-vert}{Number of Edges and Vertices}{../plots/across-country/Average DegreeAverage Excess Degree.pdf}{degree-excess}{Average Degree and Excess Degree}
 
-When compared to other countries, the US has a much larger average number of edges, and has the second smallest average distance.
-These results are not surprising, since legislators in the US are highly connected, so the distances between any random two people in the same clumps are much less compared to that of other country.
+We notice that the graph structure of the US - much like that of the UK - is separated into exclusive clusters.
+But unlike the UK, the US depicts an extreme partisonship structure in Figure \ref{fig:us_ass}.
+
+\doubleimage{}{../plots/graph/US/assortativity/assortativity_us.115.pdf}{us_ass}{US Assortativity 115}{../plots/graph/UK/assortativity/assortativity_uk.pdf}{uk_ass}{UK Assortativity}
+
+When compared to other countries, the US has a much larger average number of edges and has the second smallest average distance.
+These results are not surprising.
+Since legislators in the US are highly connected, the distance between any two random people in the same cluster is much less compared to that of other countries.
 We also observe that the generated graphs reflect the underlying structure of governance.
-For example, from Figure \ref{fig:fr_assortativity} we notice that the pink component has a single central actor, and one can thus make an educated guess that the cluster represents the French Socialist Party.
+For example, from the France graph in Figure \ref{fig:fr_assortativity} we notice that the pink component has a single central legislator, and one can thus make an educated guess that the cluster represents the French Socialist Party.
 
-\image[0.3]{../plots/graph/france/assortativity/assortativity_net_fr_an2012-2017.pdf}{fr_assortativity}{France Assortativity 2012-2017}
-
-% US graph is almost completely connected. Fully connected graphs have $n(n-1)/2$ edges. There are about 100,000 edges and 552 vertices. A complete graph would have 152,076. So this is about 67\%.
-%To-do check if this is really true because kind of unclear
+%
 
@@
 Positive assortativity measures means that nodes tend to associate more with nodes with similar attributes, while negative assortativity means that nodes associate with nodes with different attributes.
-The US assortativity value is very close to 0, which indicates that there is no preference in either direction.
+The net US assortativity value is very close to 0, which indicates that there is no overall preference in either direction.
 
 %To-do check US database
-\image[0.3]{../plots/assortativity/all_countries.pdf}{ass}{All-Country Assortativity Measures}
+\doubleimage{}{../plots/graph/france/assortativity/assortativity_net_fr_an2012-2017.pdf}{fr_assortativity}{France Assortativity 2012-2017}{../plots/assortativity/all_countries.pdf}{ass}{All-Country Assortativity Measures}
 
-We also expect that each country should exhibit power-law distributions, as there should exist hubs of legislative members with very high degree centralities.
-This turns out to be the case for smaller less densley connected graphs such as Sweden in Figure \ref{fig:se_deg}.
+We also expect that each country should exhibit power-law distributions, as there should exist hubs within legislative members with very high degree centralities.
+This turns out to be the case for smaller less densely connected graphs such as Sweden in Figure \ref{fig:se_deg}.
 However, this does not hold true for largely connected graphs such as the US, as seen in Figure \ref{fig:us_deg}.
-The US graph is almost a completely connected graph; Fully connected graphs have $n(n-1)/2$ edges.
+The US graph is almost a completely connected graph, where fully connected graphs have $n(n-1)/2$ edges.
 There are roughly 100,000 edges and 552 vertices in our US graph.
-In this case a complete graph would have 152,076, so the US is about 67\% of a fully connected graph.
+In this case a complete graph would have 152,076 edges, so the US data holds about 67\% of expected edges when compared to a fully connected graph.
 
-\image[0.3]{../plots/distributions/sweden/degree/degree_net_se2014-2018.graphml.png}{se_deg}{Sweden Degree Distribution 2014-2018}
-\image[0.3]{../plots/distributions/us/degree/degree_us.115.graphml.png}{us_deg}{US Degree Distribution 115}
+\doubleimage{}{../plots/distributions/us/degree/degree_us.115.graphml.png}{us_deg}{US Degree Distribution 115}{../plots/distributions/sweden/degree/degree_net_se2014-2018.graphml.png}{se_deg}{Sweden Degree Distribution 2014-2018}
 
@@
 The dynamic social relationships between legislators - of forging new relationships and maintaining older established relationships - matter.
-Moreover, our generated outputs hints at past and ongoing events that impact legislative cosponsorships.
-For example, the drop in number of cosponsorships across different parties in 2014-2018 in Sweden reflects the events that unfolded during the 2014 general elections.
+Moreover, changes in network properties can hint at past and ongoing events that impact legislative cosponsorships.
+
+It should be noted that network properties - such as path length and clustering coefficient - of major developed countries like the US and France tend to show little fluctuation over time.
+These consistencies can suggest that the changes in governance do not have major influences on the quality of legislative processes, which is a positive sign because these developed countries have proven working systems of governance, democracy, and law.
+
 We have uncovered some intriguing results.
@@
 One interpretation of this result is that members tend to be more isolated and fewer are willing to cooporate outside of their local network.
-As the world gets larger, the friendship circles that define and maintain social relationships grow.
-As communication between legislators improves, links become increasingly more interconnected, and the relative distance between any two given legislators decreases.
+As the world gets larger, the communities that define and maintain social relationships grow.
+As communication between legislators improves, links become increasingly interconnected, and the relative distance between any two given legislators decreases.
 This underlying phenomenom is reflected in the comparison of clustering coefficients across countries.
 For example, small countries like Austria or Denmark have low clustering coefficients of 0 and 0.2 respectively, whereas a large country like the US has a clustering coefficient of nearly 1.
+
 We also notice extreme partisanship in the US senate, which is expected given the party division and clashes between the Republicans and Democrats.
-The two components of the graph also represent the house and the senate.
-The house and the senate differ from an institutional design and have contrasting social structures, and so we would expect the behaviour in these two components to exhibit unique characteristics as well.
+The two components of the assortativity graph represent the house and the senate.
+The house and the senate differ from an institutional design standpoint and have contrasting social structures, and so we would expect the behavior in these two components to exhibit unique characteristics as well.
 Although we did not conduct any direct tests, the house and senate should differ in quantities such as clustering coefficient and average path length.
-Lastly, we examined the degree distributions of every graph, and expected that they follow power-law distributions. As it turns out, this does not hold true for large densley connected graphs.
 
-\begin{thebibliography}{9}
+Lastly, we examined the degree distributions for every graph, and hypothesized that they would follow power-law distributions.
+As it turns out, this does not hold true for large densely connected graphs and non scale-free networks.
 
-\bibitem{briatte} Briatte, Francois. ``Bill cosponsorship networks in European parliaments.'' 2016. \url{https://github.com/briatte/parlnet}.
+% \begin{thebibliography}{9}
 
-\bibitem{denmark} ``Denmark.'' \emph{Forbes}, Forbes Magazine, \url{www.forbes.com/places/denmark/}
+% \bibitem{briatte} Briatte, Francois. ``Bill cosponsorship networks in European parliaments.'' 2016. \url{https://github.com/briatte/parlnet}.
 
-\bibitem{fowler1} Fowler, James H. ``Connecting the Congress: A Study of Cosponsorship Network.'' 2006. \url{http://fowler.ucsd.edu/best_connected_congressperson.pdf}.
+% \bibitem{denmark} ``Denmark.'' \emph{Forbes}, Forbes Magazine, \url{www.forbes.com/places/denmark/}
 
-\bibitem{fowler} Fowler, J. H., Waugh, A.S., and Sohn, Y. ``Cosponsorship Network.'' 2010. \url {http://jhfowler.ucsd.edu/cosponsorship.htm}
+% \bibitem{fowler1} Fowler, James H. ``Connecting the Congress: A Study of Cosponsorship Network.'' 2006. \url{http://fowler.ucsd.edu/best_connected_congressperson.pdf}.
 
-\bibitem{switzerland} ``Switzerland country profile.'' \emph{BBC News}, BBC, 22 May 2018. \url{https://www.bbc.com/news/world-europe-17980650}
+% \bibitem{fowler} Fowler, J. H., Waugh, A.S., and Sohn, Y. ``Cosponsorship Network.'' 2010. \url {http://jhfowler.ucsd.edu/cosponsorship.htm}
 
-\bibitem{UK} UK Parliament. \url{https://edm.parliament.uk/}
+% \bibitem{switzerland} ``Switzerland country profile.'' \emph{BBC News}, BBC, 22 May 2018. \url{https://www.bbc.com/news/world-europe-17980650}
 
-\bibitem{US} United States Congress. \url{https://github.com/unitedstates/congress}
-\end{thebibliography}
+% \bibitem{UK} UK Parliament. \url{https://edm.parliament.uk/}
+
+% \bibitem{US} United States Congress. \url{https://github.com/unitedstates/congress}
+% \end{thebibliography}
 

### 2018-12-11 paper/paper.tex
paper done

@@
 
-% \begin{thebibliography}{9}
+\begin{thebibliography}{9}
 
-% \bibitem{briatte} Briatte, Francois. ``Bill cosponsorship networks in European parliaments.'' 2016. \url{https://github.com/briatte/parlnet}.
+\bibitem{briatte} Briatte, Francois. ``Bill cosponsorship networks in European parliaments.'' 2016. \url{https://github.com/briatte/parlnet}.
 
-% \bibitem{denmark} ``Denmark.'' \emph{Forbes}, Forbes Magazine, \url{www.forbes.com/places/denmark/}
+\bibitem{denmark} ``Denmark.'' \emph{Forbes}, Forbes Magazine, \url{www.forbes.com/places/denmark/}
 
-% \bibitem{fowler1} Fowler, James H. ``Connecting the Congress: A Study of Cosponsorship Network.'' 2006. \url{http://fowler.ucsd.edu/best_connected_congressperson.pdf}.
+\bibitem{fowler1} Fowler, James H. ``Connecting the Congress: A Study of Cosponsorship Network.'' 2006. \url{http://fowler.ucsd.edu/best_connected_congressperson.pdf}.
 
-% \bibitem{fowler} Fowler, J. H., Waugh, A.S., and Sohn, Y. ``Cosponsorship Network.'' 2010. \url {http://jhfowler.ucsd.edu/cosponsorship.htm}
+\bibitem{fowler} Fowler, J. H., Waugh, A.S., and Sohn, Y. ``Cosponsorship Network.'' 2010. \url {http://jhfowler.ucsd.edu/cosponsorship.htm}
 
-% \bibitem{switzerland} ``Switzerland country profile.'' \emph{BBC News}, BBC, 22 May 2018. \url{https://www.bbc.com/news/world-europe-17980650}
+\bibitem{switzerland} ``Switzerland country profile.'' \emph{BBC News}, BBC, 22 May 2018. \url{https://www.bbc.com/news/world-europe-17980650}
 
-% \bibitem{UK} UK Parliament. \url{https://edm.parliament.uk/}
+\bibitem{UK} UK Parliament. \url{https://edm.parliament.uk/}
 
-% \bibitem{US} United States Congress. \url{https://github.com/unitedstates/congress}
-% \end{thebibliography}
+\bibitem{US} United States Congress. \url{https://github.com/unitedstates/congress}
+\end{thebibliography}
 
